Model of lens candidates from Space Warps CFHTLS

### 2016-06-24 paper2.tex
edits

\begin{figure}
  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
  \caption{}
  \label{fig:SW19}
\end{figure}

\begin{figure}
  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
  \caption{}
  \label{fig:SW36}
\end{figure}

\begin{figure}
  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
  \caption{}
  \label{fig:SW57}
\end{figure}

\item Figures~\ref{fig:SW28}--\ref{fig:SW29} show the five most
  convincing lens candidates.

\item Figure~\ref{fig:SW42} shows a candidate that modelling indicates
  is doubtful.

\item Figures~\ref{fig:SW58} and \ref{fig:SW19} appear plausible lens
  candidates.

@@

>>>>

\begin{figure}
  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
  \caption{SW19}
  \label{fig:SW19}
\end{figure}

\begin{figure}
  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
  \caption{SW36}
  \label{fig:SW36}
\end{figure}

\begin{figure}
  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
  \caption{SW57}
  \label{fig:SW57}
\end{figure}

@@

\item Figures~\ref{fig:SW28}--\ref{fig:SW29} show the five most
  convincing lens candidates. SW28 shown in Figure~\ref{fig:SW28} is
  modelled as an arc with three blended images plus a saddle-point
  closer to the galaxy.  SW05 shown in Figure~\ref{fig:SW05} has four
  distinct images (two close to blending).  SW02, SW09 and SW29
  (Figures~\ref{fig:SW02}--\ref{fig:SW29}) have similar
  configurations, with a minimum furthest from the galaxy and three
  images blended into an arc.  All five would be massive ellipticals;
  SW05 is the most massive of all the candidates, with a galaxy-group
  scale mass.

\item Figure~\ref{fig:SW42} shows a candidate that modelling indicates
  is doubtful.  The images appears to have a similar morphology to the
  last three mentioned.  The implied mass, however, is implausibly
  high.\todo{Check photometry of this candidate.}

\item Figures~\ref{fig:SW58} and \ref{fig:SW19} appear plausible lens
  candidates.  Their morphology is similar to SW28, but the
  saddle-point counterimage is not visible.  We consider these lenses
  plausible but less convincing.
